On Combinatorial Games and de Bruijn Sequences

### 2016-09-20 infdebruijn.tex
Fixed an error in the statement of Proposition~\ref{simple-pos}

%\begin{observation}
%	$b(w)$ is a suffix of $b^*(w)$ for every $w \in L_n$.
%\end{observation}
%\begin{proof}
%	If $|b(w)|$ is not $n$, then $b_1(b(w))$ gives a word of length $n$ that ends with $b(w)$. Since
%\end{proof}

@@

\begin{proposition}\label{simple-pos}
	For a $w \in L_n$ let $l$ be the number of trailing zeros (from the left) in $w$ and $\bar{w}=b_1(w)$. Then:
	\begin{enumerate}
		\item For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes $i$ letters before $w$ as a sub-word of $w^\infty$.

		\item For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
	\end{enumerate}
\end{proposition}

>>>>

@@

\begin{proposition}\label{simple-pos}
	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$. Then For all $0 \leq i \leq |w|-l-1$ the word $\rr{\bar{w}}{i}$ comes $i+n-|w|$ letters before $w$ as a sub-word of $w^\infty$.
\end{proposition}
\begin{proof}
	Let $v=b(w)$. Looking at the definition of $b$, it is easy to see that the last $l-1$ letters of $w$ are not changed by the transformation, i.e., $v_{|v|-l-2}\cdots v_{|v|}=w_{|w|-l-2} \cdots w_{|w|}$. Furthermore, if the length of $w$ is not $n$, the previous letter does not change either, $v_{|v|-l-1}=w_{|v|-l-1}$, because $b$ expands the word by a prefix that is not all zeros before it decreases the first letter. Since $b^*$ consists of repeated applications of $b$ until the length of the resulting word divides $n$, we get that only the first application of $b$ may change the first letter of the tail of length $l$ of $w$ and that the rest of the applications of $b$ keep this tail fixed. Thus the word that precedes $w$ in the sequence shares the tail of length $l-1$ with $w$, i.e., all the windows of the required form appear just before $w$. 
\end{proof}

\begin{proposition}\label{advanced-pos}
	For a given $w \in L_n$, let $l$ be the number of trailing zeros (from the left) in $w$ and let $\bar{w}=b_1(w)$. Then For all $n-k \leq i \leq n-1$ the word $\rr{\bar{w}}{i}$ comes $i-(n-|f_3(u)| \pmod n)$ letters before the first $u \in \T{0^{m-1} (\bar{w}_{m} + 1) \bar{w}_{m+1}\cdots \bar{w}_n}_{m=i}^{n}$ such that $u \in L_n$ and  $\max\{u_1,\dots,u_{n-1}\} \leq max(w)$.
\end{proposition}
